Flat-histogram method comparison on the 2D Ising model

### 2020-05-07 ising/ising.tex
made a number of ising edits and a thesis edit.
went through the abstract and made edits.

\title{Flat-histogram method comparison on 2D Ising model
}

@@

\begin{abstract}
We examine the convergence of the stochastic approximation with a dynamic
update factor (SAD) algorithm applied to the 2D Ising model. Comparison with
stochastic approximation Monte Carlo (SAMC) and Wang-Landau (WL) methods show that SAD performs robustly and without user input knowledge of an energy range. We also compare SAD with ``production'' run WL with fixed weights which is the first of its kind recorded. Since SAD is more powerful in the common case in which the range of energies is not known in advance, the 2D Ising model presents a unique challenge since the energy range is readily known and easily discovered by WL methods.
\end{abstract}

>>>>

\title{Flat-histogram method comparison on the 2D Ising model
}

@@

\begin{abstract}
We examine the convergence of stochastic approximation with a dynamic
update factor (SAD) with other flat-histogram methods applied to the 2D
Ising model. The comparison with stochastic approximation Monte Carlo (SAMC)
and Wang-Landau (WL) methods shows that SAD performs robustly and without user
input knowledge of an energy range. We also compare SAD with WL followed by a
``production run'' with fixed weights which is the first comparison of its kind
recorded. We find that WL followed by a production run is preferable to pure WL
for preserving ergodicity and detailed balance. Since SAD is more powerful in
the common case in which the range of energies is not known in advance, the 2D
Ising model presents a unique challenge since the energy range is readily known
and easily discovered by WL methods.
\end{abstract}
